### 2020-04-18 Thesis-Chapter2-Background.tex
Work on international regs

The following is a very brief account of the regulatory environment in various jurisdictions around the world:

\newcommand{\countriesstart}{\begin{itemize}}
\newcommand{\country}[1]{\item \textbf{#1:}} % Country
\newcommand{\countriesend}{\end{itemize}}

\countriesstart
    \country{Australia} In 2018 passed its Assistance and Access bill \cite{ag_2018} \cite{newman_2018}
    \country{UK} Investigatory Powers Act \cite{legislature_2016}
    \country{EU} GDPR \cite{parliament_2016}
    \country{China} See \cite{donahue_comparative_2018}
    \country{Israel} See \cite{donahue_comparative_2018}
    \country{Japan, Korea} can't find anything
    \country{General} See \cite{budish_encryption_2018}
\countriesend

>>>>

This thesis is U.S.-focused, but \ac{EA} technologies and policies have international impacts. The following is a very
brief account of the regulatory environment in various jurisdictions around the world based primarily on a 2016 analysis
by the Library of Congress \cite{acosta_government_2016}.

\newcommand{\countriesstart}{\begin{itemize}}
\newcommand{\country}[3]{ % Name, citation, description
    \item \textbf{#1} \cite{#2} \nopagebreak

    \vspace{0.5\baselineskip} \parbox{\linewidth}{#3} \vspace{0.5\baselineskip}
}
\newcommand{\countriesend}{\end{itemize}}

\countriesstart

    \country{Five-Eyes Countries}{acosta_government_2016}{
% UK, Australia, Canada
% UK Investigatory Powers Act \cite{legislature_2016}
% Australia In 2018 passed its Assistance and Access bill \cite{ag_2018}

    \country{European Countries}{acosta_government_2016}{
% France, Belgium, Germany, Sweden, EU
% EU GDPR \cite{parliament_2016}

    \country{Asian Countries}{acosta_government_2016}{
% China, Japan, Taiwan
% China Counterterrorism Law \cite{donahue_comparative_2018}

    \country{Other Countries}{acosta_government_2016}{
% Brazil, Israel, South Africa
% Israel cybersecurity forensics and parnerships \cite{donahue_comparative_2018}

\countriesend

% For more, read donahue_comparative_2018 (Israel and China) and budish_encryption_2018 (framework for analysis
